\documentclass[10pt]{article}
\usepackage{titling}
\usepackage{enumitem}
\usepackage{tabularx} % extra features for tabular environment
\usepackage{amsmath}  % improve math presentation
\usepackage{graphicx} % takes care of graphic including machinery
\usepackage[margin=1in,letterpaper]{geometry} % decreases margins
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{cite} % takes care of citations
\usepackage[final]{hyperref} % adds hyper links inside the generated pdf file
\usepackage{datetime}
\hypersetup{
colorlinks=true,       % false: boxed links; true: colored links
linkcolor=blue,        % color of internal links
citecolor=blue,        % color of links to bibliography
filecolor=magenta,     % color of file links
urlcolor=blue
}
%++++++++++++++++++++++++++++++++++++++++

\setlength{\heavyrulewidth}{0.1em}
\newcommand{\otoprule}{\midrule[\heavyrulewidth]}
\newdate{trainingd}{27}{03}{2018}

\sloppy

\title{Deep Learning IndabaX @NUST}
\posttitle{\par\end{center}}
\preauthor{}
\author{}
\postauthor{}
\date{\today}

\begin{document}

\maketitle


\section{Motivation}
\label{sec:motivation}

The research activities at the Faculty of Computing and Informatics (FCI), Namibia University of Science and Technology (NUST\footnote{\url{www.nust.na}}),
revolve around five ($05$) \emph{research focus areas} (RFA). Among these is \emph{Big Data}, which encompasses research efforts related to
\emph{smart data infrastructure}, \emph{advanced analytics} and \emph{dependable systems} (fault-tolerant systems). The advanced analytics component strongly
relies on \emph{machine learning}, including \emph{deep learning}. As such, a one-day training in deep learning not only helps sharpen the skills of the
students partaking in that research effort, but it also participates in establishing an active community around machine learning, e.g., derive
insight from large data sets. Furthermore, this initiative contributes, nationwide, to building capacity to addressing an ever growing
challenge faced by both businesses and Government agencies; data-driven decision making.

\section{Strategy for Diversity and Inclusion}
\label{sec:diversity-and-inclusion}

First and foremost, at every level of involvement our approach has considered gender sensibly. Second, as much as possible various perspectives have been
integrated. For example, the organizing team includes views from both academia and the industry. As such the resulting programme does not focus only on the
research or academic needs. Rather, it caters to a broader swathe of needs. As for the speakers, we carefully selected speakers from academia,
Government agencies and industry to help package and deliver an introductory set of practical lectures to deep learning. Finally, our strategy to reaching out
and selecting participants will follow similar criteria.

\section{Organising Team}
\label{sec:org-team}

\begin{description}[align=left]
    \item[Lameck M. Amugongo] Big Data and Open Data enthusiast with a strong interest in AI and machine learning, he is a GSM Business Intelligence Analyst at
    Telecom Namibia and a Lecturer at NUST;
    \item[Jos\'{e} G. Quenum] He is an Associate Professor at NUST, leading the Big Data RFA at FCI. His research interests include Big Data and Distributed
    Systems;
    \item[Emilia N. Shikeenga] She is a Data Warehouse Business Intelligence Analyst at Telecom Namibia;
    \item[Annastasia Shipepe] She is a Lecturer at UNAM\footnote{University of Namibia, \url{www.unam.na}}.
\end{description}

\section{Description of our IndabaX}
\label{sec:indaba-format}

% Throughout the preliminary phase of organising this IndabaX event we reached out to colleagues at the University of Namibia (UNAM)
% in search of collaboration. As a result both the organising team and the speaker list involve members of UNAM.

The type of IndabaX we wish to organise for this training is a structured series of tutorial lectures by speakers from Namibia, followed by an open discussion
related to deep learning. Tentatively, we plan to run the training on \displaydate{trainingd}. A summary of the programme is depicted in Table~\ref{tab:prog}.
We expect around twenty five ($25$) participants for the training from both universities and the industry. To advertise for the event we shall combine several
 approaches, including outreach to lecturers and students, social media as well as any other communication means available within the Faculty.

\begin{table}[htp!]
  \caption{Summary of Programme}
  \label{tab:prog}
  \centering\small%
  \begin{tabular}{clr}
    \toprule%
    {\bfseries{Time Slot}} & {\bfseries{Topic}} & {\bfseries{Speaker}}\\
    \otoprule
    \multirow{3}*{08:30 - 09:15} & Introduction to the Bayesian Model & Dr Isak Neema\\
    && Namibia Statistics Agency\\
    % && INeema@nsa.org.na\\
    \midrule
    \multirow{3}*{09:15 - 10:00} & Introduction to Machine Learning & Dr Guy Z. Lusilao\\
    && Namibia University of Science and Technology\\
    % && gzodi@nust.na\\
    \midrule
    \multirow{3}*{10:00 - 10:30} & Introduction to Neural Networks & Prof Singh D. Jat\\
    && Namibia University of Science and Technology\\
    % && dsingh@nust.na\\
    \midrule
    \multicolumn{3}{c}{Break}\\
    \midrule
    \multirow{3}*{10:45 - 11:30} & Practical I & Lameck Amugongo\\
    & (Tensorflow \& Neural Networks)& Namibia University of Science and Technology\\
    % && lamugongo@nust.na\\
    \midrule
    \multirow{3}*{11:30 - 13:15} & Practical II & Lameck Amugongo\\
    & (Tensorflow \& Deep Neural Networks)& Namibia University of Science and Technology\\
    % && lamugongo@nust.na\\
    \midrule
    \multicolumn{3}{c}{Break}\\
    \midrule
    \multirow{3}*{14:15 - 15:00} & Deep Learning & Dr Nalina Suresh\\
    & & University of Namibia\\
    % && nsuresh@unam.na\\
    \midrule
    \multirow{8}*{15:00 - 17:00} & \multicolumn{2}{c}{\emph{Discussion on Deep Learning}}\\
    &  Data Analytics Challenges & Dr Pieter Kruger\\
    & & Standard Bank Namibia\\
    % & & Pieter.Kruger@standardbank.com.na\\
    \cmidrule{2-3}\\
    &  Programming Neural Networks on Multiple & Dr Paulus Sheetekela\\
    & Processors & University of Namibia\\
    % & & psheetekela@unam.na\\
    \bottomrule%
  \end{tabular}
\end{table}

\section{Budget}
\label{sec:budget}

\begin{center}
    \begin{tabular}{lcrr}
        \toprule
        {\bfseries{Item}} & {\bfseries{Quantity}} & {\bfseries{Unit Price}} (ZAR) & {\bfseries{Amount}} (ZAR)\\
        \otoprule
        Conference Room (Full Day) & $1$ & $3000$ & $3000$\\
        \midrule
        Coffee and Tea Break & $2\times 40$ & $15$ & $1200$\\
        \midrule
        Lunch & $40$ & $196$ & $7840$\\
        \midrule
        Advertisement & $1$ & $5000$ & $5000$\\
	\midrule\midrule
        \multicolumn{3}{c}{Total} & $17040$\\
        \bottomrule
    \end{tabular}
\end{center}


\end{document}
