\documentclass[10pt]{article}
\usepackage{titling}
\usepackage{enumitem}
\usepackage{tabularx} % extra features for tabular environment
\usepackage{amsmath}  % improve math presentation
\usepackage{graphicx} % takes care of graphic including machinery
\usepackage[margin=1in,letterpaper]{geometry} % decreases margins
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{cite} % takes care of citations
\usepackage[final]{hyperref} % adds hyper links inside the generated pdf file
\usepackage{datetime}
\hypersetup{
colorlinks=true,       % false: boxed links; true: colored links
linkcolor=blue,        % color of internal links
citecolor=blue,        % color of links to bibliography
filecolor=magenta,     % color of file links
urlcolor=blue
}
%++++++++++++++++++++++++++++++++++++++++

\setlength{\heavyrulewidth}{0.1em}
\newcommand{\otoprule}{\midrule[\heavyrulewidth]}
\newdate{trainingd}{23}{04}{2019}

\sloppy

\title{Deep Learning IndabaX @NUST}
\posttitle{\par\end{center}}
\preauthor{}
\author{}
\postauthor{}
\date{\today}

\begin{document}

\maketitle


\section{Motivation}
\label{sec:motivation}

\emph{Big Data} is one of the \emph{research focus areas} (RFA) at the Faculty of Computing and Informatics (FCI), Namibia University of Science and Technology (NUST\footnote{\url{www.nust.na}}). It focuses its research efforts on \emph{smart data infrastructure}, \emph{advanced analytics} and \emph{dependable systems} (fault-tolerant systems). The \emph{Advanced Analytics} component also promotes \emph{machine learning}, including \emph{deep learning}.

In 2018, thanks to the IndabaX initiative and funding, we organised a one-day training on machine learning and deep learning. The event helped create awareness about machine learning and deep learning and sharpen the skills of the students actively contributing to the research effort. It also provided the stepping stones for building an active community around deep learning and big data. Building on the success from last year, we wish to organise a similar event this year, blending practical sessions and theoretical discussions on the advances in deep learning. Activities of this kind will undoubtedly contribute, nationwide, to building capacity to addressing an ever growing
challenge faced by both businesses and Government agencies; data-driven decision making.

\section{Strategy for Diversity and Inclusion}
\label{sec:diversity-and-inclusion}

First and foremost, at every level of involvement, our approach has considered gender sensibly. Second, as much as possible, various perspectives have been
integrated. For example, the organising team includes views from both academia and the industry. As such the resulting programme does not focus only on the
research or academic needs. Instead, it caters to a broader swathe of needs. As for the speakers, we carefully selected speakers from academia,
Government agencies and industry to help package and deliver a set of practical lectures to deep learning as well as recent advances in the field. Finally, our strategy for reaching out
and selecting participants will follow similar criteria.

\section{Organising Team}
\label{sec:org-team}

\begin{description}[align=left]
    \item[Lameck M. Amugongo] Big Data and Open Data enthusiast with a strong interest in AI and machine learning, he is a GSM Business Intelligence Analyst at
    Telecom Namibia and a Lecturer at NUST;
    \item[Suoma Hangula] She holds a Bachelor degree Honours in Comoputer Science;
    \item[Cameron Macrae] He is a Lecturer at NUST. His research interests include machine learning, optimisation andf data analytics;
    \item[Jos\'{e} G. Quenum] He is an Associate Professor at NUST, leading the Big Data RFA at FCI. His research interests include Big Data and Distributed
    Systems;
    \item[Annastasia Shipepe] She is a Lecturer at UNAM\footnote{University of Namibia, \url{www.unam.na}};
    
\end{description}

\section{Description of our IndabaX}
\label{sec:indaba-format}

% Throughout the preliminary phase of organising this IndabaX event we reached out to colleagues at the University of Namibia (UNAM)
% in search of collaboration. As a result both the organising team and the speaker list involve members of UNAM.

The type of IndabaX we wish to organise for this training is a structured series of tutorial lectures by speakers from Namibia, followed by a review of theoretical advances in deep learning. Tentatively, we plan to run the training on \displaydate{trainingd}. A summary of the programme is depicted in Table~\ref{tab:prog}.
We expect around twenty five ($40$) participants for the training from both universities and the industry. To advertise for the event we shall combine several
 approaches, including outreach to lecturers and students, social media as well as any other communication means available within the Faculty.

\begin{table}[htp!]
  \caption{Summary of Programme}
  \label{tab:prog}
  \centering\small%
  \begin{tabular}{clr}
    \toprule%
    {\bfseries{Time Slot}} & {\bfseries{Topic}} & {\bfseries{Speaker}}\\
    \otoprule
    \multirow{4}*{08:30 - 10:30} & Deep Learning Tutorial I & Dr Cameron Macrae\\
    && Dr Guy Z. Lusilao\\
    && Prof. Jos\'{e} G. Quenum\\
    && Namibia University of Science and Technology\\
    \midrule
    \multicolumn{3}{c}{Coffee Break}\\
    \midrule
    \multirow{4}*{10:45 - 13:15} & Deep Learning Tutorial II & Dr Cameron Macrae\\
    && Dr Guy Z. Lusilao\\
    && Prof. Jos\'{e} G. Quenum\\
    && Namibia University of Science and Technology\\
    \midrule
    \multicolumn{3}{c}{Lunch Break}\\
    \midrule
    \multirow{3}*{14:15 - 15:15} & Big Data Challenges in Namibian Organisations & Mr Pieter Kruger\\
    & & Standard Bank Namibia\\
    \midrule
    \multicolumn{3}{c}{Coffee Break}\\
    \midrule
    \multirow{11}*{15:30 - 17:00} & \multicolumn{2}{c}{\emph{Advances in Deep Learning}}\\
    &  ANN Architecture for Deep Learning & Dr Nalina Suresh\\
    & & University of Namibia\\
    \cmidrule{2-3}\\
    &  Deep Learning Applications& Prof. Dharm S. Jat\\
    && Namibia University of Science and Technology\\
    \cmidrule{2-3}\\
    &  Deep Learning and IoT & Dr Paulus Sheetekela\\
    && International University of Management\\
    \bottomrule%
  \end{tabular}
\end{table}

\section{Budget}
\label{sec:budget}

\begin{center}
    \begin{tabular}{lcrr}
        \toprule
        {\bfseries{Item}} & {\bfseries{Quantity}} & {\bfseries{Unit Price}} (ZAR) & {\bfseries{Amount}} (ZAR)\\
        \otoprule
        Conference Room (Full Day) & $1$ & $3000$ & $3000$\\
        \midrule
        Coffee and Tea Break & $2\times 50$ & $15$ & $1500$\\
        \midrule
        Lunch & $50$ & $196$ & $9800$\\
        \midrule
        Advertisement & $1$ & $5000$ & $5000$\\
	\midrule\midrule
        \multicolumn{3}{c}{Total} & $19300$\\
        \bottomrule
    \end{tabular}
\end{center}


\end{document}
